A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness

### 2019-04-23 Paper_neural_coarse_graining_of_consciousness.tex
1. Deleted unnecessary newline 2. Fixed misplaced alignment tab characters & --> \&

		\noindent
		We first hypothesise that, at given time $t$, levels of consciousness $C_{t}^{Level}$ corresponds to the degree of  $NTIC_{t}$ at a coarse-grained level.
			\begin{equation}\label{eq:cLevel}
				C_{t}^{Level} = NTIC_{t}
			\end{equation}

		\newline
		\noindent 
		We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
			\begin{equation}\label{eq:cContent}
				C_{t}^{Content} = Y_{t}
			\end{equation}

@@

				@ \rewrite{According to Noë, perceptual presence is explained by a “ sensorimotor theory ” on which perception depends on a practical mastery of sensorimotor dependencies or “ sensorimotor contingencies ” (SMCs) (O ’ Regan & Noë, 2001). The theory inherits from Gibsonian notions of “ affordances ” (Gibson, 1979) and from enactive cognitive science (Thompson & Varela, 2001) which stress the importance of brain-body-world interactions in cognitive processes. On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations. A strong point of this theory is that it suggests why there are differences in qualitative character between modalities, the reason being that different modalities instantiate different SMCs (O ’ Regan & Noë, 2001). }

>>>>

		\noindent
		We first hypothesise that, at given time $t$, levels of consciousness $C_{t}^{Level}$ corresponds to the degree of  $NTIC_{t}$ at a coarse-grained level.
			\begin{equation}\label{eq:cLevel}
				C_{t}^{Level} = NTIC_{t}
			\end{equation}
		\newline
		\noindent 
		We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
			\begin{equation}\label{eq:cContent}
				C_{t}^{Content} = Y_{t}
			\end{equation}

@@

				@ \rewrite{According to Noë, perceptual presence is explained by a “ sensorimotor theory ” on which perception depends on a practical mastery of sensorimotor dependencies or “ sensorimotor contingencies ” (SMCs) (O ’ Regan \& Noë, 2001). The theory inherits from Gibsonian notions of “ affordances ” (Gibson, 1979) and from enactive cognitive science (Thompson \& Varela, 2001) which stress the importance of brain-body-world interactions in cognitive processes. On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations. A strong point of this theory is that it suggests why there are differences in qualitative character between modalities, the reason being that different modalities instantiate different SMCs (O ’ Regan \& Noë, 2001). }
